---
format: revealjs
---

# Example Presentation

**How to use `quartoMorphSvg`**

Installing package:

```{r}
#| echo: true
#| output: false
if(!"quartoMorphSvg" %in% rownames(installed.packages())){
  devtools::install_github("klingelhoefer/quartoMorphSvg")
}
library(quartoMorphSvg)
```

To display an image, you can simply write inline (replace with your path(s):

```{r}
#| eval: false
#| echo: true
`r morph_svg("path/to/img_1.svg", "path/to/img_1.svg")` 
```

## Moderation Example

`r morph_svg("images/moderation/Slide1.svg", "images/moderation/Slide2.svg", height = "400px")`

To generate the image above:

```{r}
#| eval: false
#| echo: true
`r morph_svg(folder = "images/moderation, height = "400px")`
```

## Mediation Example

```{r}
#| echo: true
morph_svg(
  folder = "images/mediation", 
  height = "12em", 
  animation_duration = .5, 
  animation_curve = "cubic-bezier(0.76, 0, 0.24, 1)"
)
```

## Tidyverse Logo Example

::: columns
::: {.column width="60%"}
Any order can be specified/repeated an arbitrary amount of times, e.g.,

```{r}
#| eval: false
#| echo: true
`r morph_svg("images/tidyverse/1.svg", "images/tidyverse/2.svg", "images/tidyverse/3.svg", "images/tidyverse/2.svg", "images/tidyverse/1.svg", height = "12em")`
```

Note that complex images may take a while to render
:::

::: {.column width="40%"}
`r morph_svg("images/tidyverse/1.svg", "images/tidyverse/2.svg", "images/tidyverse/3.svg", "images/tidyverse/2.svg", "images/tidyverse/1.svg", height = "12em", animation_duration = .75)`
:::
:::

## Monstera Example

::: columns
::: {.column width="35%"}
The generated output can be used in any other HTML document, and even standalone. In non-quarto documents it will only react to clicking, thus, `click` should be `TRUE` (the default).
:::
::: {.column width="65%"}
`r morph_svg(folder = "images/monstera/", animation_duration = 1.25, click = F, height = "12em")`
```{r}
#| eval: false
#| echo: true
`r morph_svg(folder = "images/monstera/", animation_duration = 1.25, click = F, height = "14em")`
```
:::
:::




